Defocus Corrected Large Area Cryo-EM (DeCo-LACE) for Label-Free Detection of Molecules across Entire Cell Sections

### 2022-05-20 figures/initmatching.tex
Final fix [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/e94f17b00fe53a7b703becda30c7a1b1503e6e7e.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/e94f17b00fe53a7b703becda30c7a1b1503e6e7e/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2355518964

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{19cm} 
    \newcommand{\figheight}{10cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

\node (anchor) at (6.5,9.35) {}; 
\node[labelNode] {B};
\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/30_matches.png}};
\node (n3) [box=green, fit=(img)] {};

\node (anchor) at (12.75,9.35) {}; 
\node[labelNode] {C};
\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/506_matches.png}};
\node (n3) [box=red, fit=(img)] {};

\node (anchor) at (6.5,4.75) {}; 
\node[labelNode] {D};
\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/17_matches.png}};
\node (n3) [box=orange, fit=(img)] {};

\node (anchor) at (12.75,4.75) {}; 
\node[labelNode] {E};
\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/52_matches.png}};
\node (n3) [box=magenta, fit=(img)] {};

>>>>

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{calc}
    \def\centerarc[#1](#2)(#3:#4:#5){ \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
    \usetikzlibrary{3d}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{19cm} 
    \newcommand{\figheight}{10cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

\node (anchor) at (6.5,9.35) {}; 
\node[labelNode] {B};
\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/30_matches_m.png}};
\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/30_matches.png}};
\node (n3) [box=green, fit=(img)] {};

\node (anchor) at (12.75,9.35) {}; 
\node[labelNode] {C};
\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/506_matches_m.png}};
\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/506_matches.png}};
\node (n3) [box=red, fit=(img)] {};

\node (anchor) at (6.5,4.75) {}; 
\node[labelNode] {D};
\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/17_matches_m.png}};
\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/17_matches.png}};
\node (n3) [box=orange, fit=(img)] {};

\node (anchor) at (12.75,4.75) {}; 
\node[labelNode] {E};
\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/52_matches_m.png}};
\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/52_matches.png}};
\node (n3) [box=magenta, fit=(img)] {};

### 2022-05-20 figures/lamella_images.tex
Final fix [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/e94f17b00fe53a7b703becda30c7a1b1503e6e7e.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/e94f17b00fe53a7b703becda30c7a1b1503e6e7e/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2355518964

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{20.0cm} 
    \newcommand{\figheight}{5cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

    \def\panelheight{4.6cm}

\node (anchor) at (0.5,4.5) {}; 
\node[labelNode] {A};
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/slicer000.png}};
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/slicer001.png}};
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/slicer002.png}};
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/slicer003.png}};

\node (anchor) at ([shift={(0.0cm,-0.5cm)}]0.5,0 |- panel.south) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/slicer005.png}};
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/slicer006.png}};
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/slicer007.png}};
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/slicer008.png}};

>>>>

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{calc}
    \def\centerarc[#1](#2)(#3:#4:#5){ \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
    \usetikzlibrary{3d}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{20.0cm} 
    \newcommand{\figheight}{5cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

    \newlength{\panelheight}
\setlength{\panelheight}{4.4cm}

\node (anchor) at (0.5,4.5) {}; 
\node[labelNode] {A};
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/euc_lamella1_view.png}};
% Title
\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{EUC}$ 1};
% scalebar - physical height is 12810 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 12.81 , yshift=0.3cm]panel.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 12.81, yshift=0.3cm]panel.south west);
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/euc_lamella2_view.png}};
% Title
\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{EUC}$ 2};
% scalebar - physical height is 7027.5 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 7.0275 , yshift=0.3cm]panel.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 7.0275, yshift=0.3cm]panel.south west);
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/euc_lamella3_view.png}};
% Title
\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{EUC}$ 3};
% scalebar - physical height is 9615 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.615 , yshift=0.3cm]panel.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.615, yshift=0.3cm]panel.south west);
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/euc_lamella4_view.png}};
% Title
\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{EUC}$ 4};
% scalebar - physical height is 8625 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 8.625 , yshift=0.3cm]panel.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 8.625, yshift=0.3cm]panel.south west);

\node (anchor) at ([shift={(0.0cm,-0.5cm)}]0.5,0 |- panel.south) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/fff_lamella1_view.png}};
% Title
\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{FFF}$ 1};
% scalebar - physical height is 8032.5 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 8.0325 , yshift=0.3cm]panel.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 8.0325, yshift=0.3cm]panel.south west);
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/fff_lamella2_view.png}};
% Title
\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{FFF}$ 2};
% scalebar - physical height is 10000.5 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 10.0005 , yshift=0.3cm]panel.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 10.0005, yshift=0.3cm]panel.south west);
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/fff_lamella3_view.png}};
% Title
\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{FFF}$ 3};
% scalebar - physical height is 9975 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.975 , yshift=0.3cm]panel.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.975, yshift=0.3cm]panel.south west);
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/fff_lamella4_view.png}};
% Title
\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{FFF}$ 4};
% scalebar - physical height is 9337.5 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.3375 , yshift=0.3cm]panel.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.3375, yshift=0.3cm]panel.south west);

\node (anchor) at ([shift={(0.0cm,-1.0cm)}]0.5,0 |- panel.south) {}; 
\node[labelNode] {B};
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/euc_lamella1_assm.png}};
% Title
\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{EUC}$ 1: 909 tiles};
% scalebar - physical height is 12810 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 12.81 , yshift=0.3cm]panel.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 12.81, yshift=0.3cm]panel.south west);
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/euc_lamella2_assm.png}};
% Title
\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{EUC}$ 2: 451 tiles};
% scalebar - physical height is 7027.5 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 7.0275 , yshift=0.3cm]panel.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 7.0275, yshift=0.3cm]panel.south west);
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/euc_lamella3_assm.png}};
% Title
\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{EUC}$ 3: 513 tiles};
% scalebar - physical height is 9615 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.615 , yshift=0.3cm]panel.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.615, yshift=0.3cm]panel.south west);
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/euc_lamella4_assm.png}};
% Title
\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{EUC}$ 4: 497 tiles};
% scalebar - physical height is 8625 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 8.625 , yshift=0.3cm]panel.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 8.625, yshift=0.3cm]panel.south west);

\node (anchor) at ([shift={(0.0cm,-0.5cm)}]0.5,0 |- panel.south) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/fff_lamella1_assm.png}};
% Title
\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{FFF}$ 1: 438 tiles};
% scalebar - physical height is 10000.5 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 10.0005 , yshift=0.3cm]panel.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 10.0005, yshift=0.3cm]panel.south west);
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/fff_lamella2_assm.png}};
% Title
\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{FFF}$ 2: 474 tiles};
% scalebar - physical height is 10000.5 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 10.0005 , yshift=0.3cm]panel.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 10.0005, yshift=0.3cm]panel.south west);
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/fff_lamella3_assm.png}};
% Title
\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{FFF}$ 3: 501 tiles};
% scalebar - physical height is 9975 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.975 , yshift=0.3cm]panel.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.975, yshift=0.3cm]panel.south west);
\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/fff_lamella4_assm.png}};
% Title
\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{FFF}$ 4: 425 tiles};
% scalebar - physical height is 9337.5 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.3375 , yshift=0.3cm]panel.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.3375, yshift=0.3cm]panel.south west);

\newlength{\padding}
\setlength{\padding}{0.2cm}
\node (anchor) at ([shift={(0.0cm,-1.0cm)}]0.5,0 |- panel.south) {}; 
\node[labelNode] {C};
\node[graphicNode] (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap004.png}};
\node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap012.png}};
\node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap015.png}};
\node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap020.png}};
\node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
\node[graphicNode] (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap006.png}};

\node (anchor) at ([shift={(0.0cm,-\padding)}]0.5,0 |- panel.south) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap021.png}};
\node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap022.png}};
\node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap027.png}};
\node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap029.png}};
\node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
\node[graphicNode]  (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap023.png}};
% scalebar - physical height is 375 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + 0.75\panelheight / 3.75 , yshift=0.3cm]panel.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + 0.75\panelheight / 3.75, yshift=0.3cm]panel.south west);

### 2022-05-20 figures/matching_euc.tex
Final fix [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/e94f17b00fe53a7b703becda30c7a1b1503e6e7e.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/e94f17b00fe53a7b703becda30c7a1b1503e6e7e/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2355518964

\node (anchor) at (0.5,9.5) {}; 
\node[labelNode] {A};
\node[graphicNode] {\includegraphics[height=12cm]{content/images/euc_lamella1_1000px.png}};
\node[graphicNode] {\includegraphics[height=12cm]{content/images/euc_lamella1_just_matches.png}};

\node (anchor) at (11.0,9.5) {}; 
\node[labelNode] {B};
\node[anchor=north west, below right=0cm and -4.5cm of anchor] {\includegraphics[height=12cm]{content/images/euc_lamella1_just_matches_side.png}};

\node (anchor) at (13.0,9.5) {}; 
\node[labelNode] {C};
\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/euc_lamella1_just_matches_er_ribos.png}};

\node (anchor) at (13.0,6.5) {}; 
\node[labelNode] {D};
\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/euc_lamella1_just_matches_nucleus.png}};

\node (anchor) at (13.,3.5) {}; 
\node[labelNode] {E};
\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/euc_lamella1_just_matches_circle.png}};

\node (anchor) at (13.0,0.5) {}; 
\node[labelNode] {F};
\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/euc_lamella1_just_matches_contained.png}};

>>>>

    \newlength{\panelheight}
\setlength{\panelheight}{12cm}

\node (anchor) at (0.5,9.5) {}; 
\node[labelNode] {A};
\node[graphicNode] (assm) {\includegraphics[height=\panelheight]{content/images/euc_lamella1_assm.png}};
\node[graphicNode] {\includegraphics[height=\panelheight]{content/images/euc_lamella1.png}};
\node (rect) at (7.4,3.5) [anchor=center,draw,thick,minimum width=0.3cm,minimum height=0.3cm,color=red] {};
\node (rect) at (1.75,4.5) [anchor=center,draw,thick,minimum width=0.3cm,minimum height=0.3cm,color=green] {};
\node (rect) at (7.2,2.15) [anchor=center,draw,thick,minimum width=0.3cm,minimum height=0.3cm,color=blue!60] {};
\node (rect) at (6.45,6.0) [anchor=center,draw,thick,minimum width=0.47cm,minimum height=0.47cm,color=cyan] {};
% scalebar - physical height is 12810 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]assm.south west) -- ([xshift=0.5cm + \panelheight / 12.81 , yshift=0.3cm]assm.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]assm.south west) -- ([xshift=0.5cm + \panelheight / 12.81, yshift=0.3cm]assm.south west);

\node (anchor) at (11.0,9.5) {}; 
\node[labelNode] {B};
\node[anchor=north west, below right=0cm and 0.0cm of anchor] (side) {\includegraphics[height=12cm, trim=20.5cm 0 2cm 0]{content/images/euc_lamella1_side.png}};

\draw [->, thick] ($ (assm.east) + (0.1,0) $) -- node[above=0.2cm, align=center] (c) {} ($ (side.west) + (0.2,0) $);

\centerarc [canvas is zx plane at y=0.75, ->](c.center)(-90:180:0.15);
\draw [very thick] ($ (c.center) + (0,-0.1) $) -- ($ (c.center) + (0,0.2) $);
\node at ($ (c.center) + (0.5,0) $) {90°};

\newlength{\panelheightm}
\setlength{\panelheightm}{2.8cm}
\node (anchor) at (13.0,9.5) {}; 
\node[labelNode] {C};
\node[graphicNode] (pan) {\includegraphics[height=\panelheightm]{content/images/euc_lamella1_detail1.png}};
\node (n3) [box=red, fit=(pan)] {};
% scalebar - physical height is 300 nm
\draw [line width=1.55mm,white] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 3 , yshift=0.2cm]pan.south west);
\draw [line width=0.7mm,black] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 3, yshift=0.2cm]pan.south west);

\node (anchor) at (13.0,6.5) {}; 
\node[labelNode] {D};
\node[graphicNode] (pan) {\includegraphics[height=\panelheightm]{content/images/euc_lamella1_detail2.png}};
\node (n3) [box=green, fit=(pan)] {};

% scalebar - physical height is 300 nm
\draw [line width=1.55mm,white] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 3 , yshift=0.2cm]pan.south west);
\draw [line width=0.7mm,black] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 3, yshift=0.2cm]pan.south west);

\node (anchor) at (13.,3.5) {}; 
\node[labelNode] {E};
\node[graphicNode] (pan) {\includegraphics[height=\panelheightm]{content/images/euc_lamella1_detail3.png}};
\node (n3) [box=blue!60, fit=(pan)] {};

% scalebar - physical height is 300 nm
\draw [line width=1.55mm,white] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 3 , yshift=0.2cm]pan.south west);
\draw [line width=0.7mm,black] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 3, yshift=0.2cm]pan.south west);

\node (anchor) at (13.0,0.5) {}; 
\node[labelNode] {F};
\node[graphicNode] (pan) {\includegraphics[height=\panelheightm]{content/images/euc_lamella1_detail4.png}};
\node (n3) [box=cyan, fit=(pan)] {};

% scalebar - physical height is 500 nm
\draw [line width=1.55mm,white] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 5 , yshift=0.2cm]pan.south west);
\draw [line width=0.7mm,black] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 5, yshift=0.2cm]pan.south west);
